\input{./._relpath-to-latexroot.ltx}
\documentclass[\latexroot/\projectname]{subfiles}
\input{\latexroot/@resources/subfile-setup.ltx}
\begin{document}

\section{Conclusion}\whenintegrated{\label{conclusion}}
\whenintegrated{\label{sec:conclusion}} % integrated doc: SST for labels

This paper studies the transmission of conventional and unconventional monetary policy in Mexico. Using high-frequency identification techniques, we distinguish between MP, CBI, and RN shocks embedded in two types of interest rate surprises around policy announcements: target-rate surprises, which capture unexpected changes in the current policy rate, and FG surprises, which reflect revisions to the expected future path of the policy rate. We then estimate the macroeconomic effects of these shocks using a monthly VAR.

We show that failing to disentangle CBI and RN components leads to biased estimates of monetary policy effects, giving rise to counterintuitive results such as expansions in output, rising prices, a depreciation of the domestic currency, and increases in inflation expectations following contractionary target-rate shocks. Once these components are isolated, these anomalies largely disappear. In response to contractionary pure target-rate shocks,  output and prices exhibit a hump-shaped decline, the domestic currency appreciates, and inflation expectations remain well anchored. For unconventional policy, unpurged FG shocks appear to have disproportionately large and immediate effects on economic activity. In addition, inflation expectations tend to rise in response to contractionary FG shocks. Once CBI and RN components are removed, however, the effects of these shocks become more moderate and closely resemble those of pure target-rate shocks. We also show that CBI and RN shocks play distinct contamination roles across policy instruments. While both tend to reverse the effects of target-rate shocks, RN shocks disproportionately amplify and accelerate the transmission of FG shocks, whereas CBI shocks play a more limited role.

Overall, our results highlight the importance of disentangling interest rate surprises into their structural components when studying monetary policy transmission in EMEs with characteristics similar to those of Mexico. Ignoring CBI and RN components may lead to misleading conclusions about the effectiveness of monetary policy in these economies. Regardless of the precise mechanism behind the disproportionately large and more immediate effects of unpurged FG shocks on domestic output, disentangling RN components helps mitigate these distortions and yields estimates that are more consistent with standard transmission mechanisms and the empirical evidence documented in the literature.

Future research could extend this approach to other EMEs, subject to the availability of high-frequency financial data. In addition, further work could explore how the relative importance of MP, CBI, and RN shocks evolves over time. It would also be interesting to extend this framework to incorporate other forms of central bank communication, such as policy minutes, press conferences, and speeches. An additional research avenue would be to disentangle asset purchase program surprises, given that several EMEs implemented these programs for the first time during the COVID-19 crisis.

% Smart bibliography: Only include bibliography if standalone AND has citations
\smartbib

\pdfonly{
% execute this version if compiling with pdflatex
\end{document}
}
