\input{./._relpath-to-latexroot.ltx}
\documentclass[\latexroot/\projectname]{subfiles}
\input{\latexroot/@resources/subfile-setup.ltx}

\begin{document}

\section{Introduction}
\whenintegrated{\label{sec:intro}} % integrated doc: SST for labels
\setcounter{page}{0}\pagenumbering{arabic}

High-frequency changes in interest rates around central bank announcements—commonly referred to as monetary policy or interest rate surprises—have become a widely used proxy for monetary policy (MP) shocks. In advanced economies (AEs), a large literature combines these surprises with vector autoregressive (VAR) models or local projections to study the macroeconomic effects of both conventional and unconventional monetary policies. Applying this methodology to emerging market economies (EMEs), however, poses additional challenges, partly reflecting the more limited availability and shorter time span of high-frequency financial data. Although recent studies have extended high-frequency identification (HFI) techniques to some EMEs, much of this literature does not distinguish between conventional and unconventional MP shocks. As a result, evidence on the macroeconomic effects of forward guidance (FG) in these economies remains limited. Moreover, several studies document puzzling responses to contractionary MP shocks, including a depreciation of the domestic currency, rising prices, and increases in inflation expectations. Such findings are difficult to reconcile with standard macroeconomic models and raise questions about the transmission of monetary policy in EMEs.


A potential explanation for these puzzling findings is that interest rate surprises may not exclusively capture MP shocks, that is, exogenous deviations from a systematic policy rule. In particular, they may also reflect \emph{central bank information (CBI) shocks} (\hyperlink{JK (2020)}{Jarociński and Karadi, 2020}), which arise when the central bank reveals new information about the economic outlook in its announcements while simultaneously adjusting the policy stance in response to that information. In addition, interest rate surprises may reflect \emph{response-to-news (RN) shocks} (\hyperlink{Bauer and Swanson (2023a)}{Bauer and Swanson, 2023a, 2023b}), which arise when markets misperceive the central bank’s policy rule and therefore underestimate or overestimate the strength of its response to observable economic developments. As emphasized in the HFI literature, failing to isolate these shocks from interest rate surprises  may lead to biased estimates of the effects of monetary policy on the economy.

This paper studies the transmission of conventional and unconventional monetary policy in an EME using HFI techniques. Focusing on Mexico as a case study, we decompose interest rate surprises around central bank announcements into MP, CBI, and RN shocks.\footnote{Mexico provides a suitable case study given its small open economy status, credible inflation-targeting regime (\hyperlink{De Pooter et al. (2014)}{De Pooter et al., 2014}; \hyperlink{Beauregard et al. (2024)}{Beauregard et al., 2024}), flexible and market-determined exchange rate (\hyperlink{Ilzetzki et al. (2019)}{Ilzetzki et al., 2019}), and relatively deep and liquid financial markets (\hyperlink{Solis (2023b)}{Solís, 2023a, 2023b}). In particular, the depth and liquidity of Mexican financial markets allow the measurement of interest rate surprises across different maturities and over a relatively long sample period—essential conditions for distinguishing between conventional and unconventional MP shocks and for increasing the overall variation in surprises. This increased variation helps address concerns raised by \hyperlink{Ramey (2016)}{Ramey (2016)} and \hyperlink{Bauer and Swanson (2023b)}{Bauer and Swanson (2023b)} that, in short samples, the macroeconomic effects of monetary policy may be imprecisely estimated.} This decomposition is applied to two types of interest rate surprises: \emph{target-rate surprises}, which capture unexpected changes in the current level of the policy rate, and \emph{FG surprises}, which reflect unexpected revisions to the future path of the policy rate. Using a monthly VAR over the period January 2002 to December 2024, we estimate the dynamic effects of these shocks on a set of macroeconomic and financial variables, including output, prices, the exchange rate, stock prices, inflation expectations, and short- and long-term interest rates.

We construct monetary policy surprises using high-frequency changes in interest rate swaps with maturities ranging from 1 to 12 months around policy announcements. These changes are measured as close-to-close movements from the day preceding the announcement to the announcement day, a standard approach in the EME literature. Following the standard approach of \hyperlink{Gürkaynak et al. (2005)}{Gürkaynak et al. (2005)}, we then extract the first two principal components (PCs) of these changes and rotate them so that the second PC has zero loading on the 1-month swap rate. After this rotation, the first factor can be interpreted as reflecting unexpected changes in the current policy rate—closely tracked by the 1-month swap rate—and we therefore label it the \emph{target-rate surprise}. The second factor captures revisions to the expected near-term policy path, that is, movements in longer-maturity swap rates that are orthogonal to changes in the current policy rate, and we refer to it as the \emph{FG surprise}. 

Following \hyperlink{Bauer and Swanson (2023a, 2023b)}{Bauer and Swanson (2023a, 2023b)}, each interest rate surprise—both target-rate and FG—is regressed on a set of public macroeconomic and financial news released prior to the policy announcement and decomposed into fitted and residual components. The fitted component captures the portion of the surprise that is predictable based on information already incorporated into expectations prior to the announcement. As emphasized by \hyperlink{Bauer and Swanson (2023a, 2023b)}{Bauer and Swanson (2023a, 2023b)}, this component may reflect a stronger or weaker than expected response of the central bank to observable economic developments, potentially arising from market misperceptions of the policy-maker's policy rule. The residual component, by contrast, isolates the portion of the surprise that is orthogonal to prior news and thus provides a cleaner proxy for MP shocks.

Building on \hyperlink{Jarociński and Karadi (2025)}{Jarociński and Karadi (2025)}, we then exploit the co-movement between interest rate and stock price surprises around policy announcements to jointly identify MP, CBI, and RN shocks embedded in both target-rate and FG surprises. Specifically, a \emph{pure MP shock} is identified by a negative co-movement between the residual component of the interest rate surprise and the stock price surprise. This pattern is consistent with an unexpected tightening that raises discount rates and lowers expected future cash flows, leading to an immediate decline in equity prices. When identification is based on the decomposition of the target-rate surprise, we generally refer to the resulting disturbance as a \emph{pure target-rate shock}; when it is based on the decomposition of the FG surprise, we generally refer to it as a \emph{pure FG shock}.

An \emph{RN shock}, in turn, is characterized by a negative co-movement between the fitted component of the interest rate surprise and the stock price surprise. This configuration captures episodes in which the central bank responds more aggressively than markets anticipated to publicly available information. Because that information was largely incorporated into expectations prior to the announcement, the only new element revealed within the announcement window is a stronger-than-expected policy response, which depresses equity prices through standard discount-rate and cash-flow channels.

Finally, a \emph{CBI shock} is associated with a positive co-movement between the interest rate surprise and the stock price surprise. This pattern may arise when the central bank reveals favorable new information about economic fundamentals while simultaneously tightening policy. In such cases, equity prices increase in response to improved growth prospects and higher expected future cash flows, despite the policy tightening.

Our main results indicate that CBI and RN components tend to attenuate—and even reverse—the estimated effects of conventional MP shocks. When these components are not disentangled, impulse responses to contractionary target-rate shocks display several of the puzzles documented in the literature, including expansions in output, rising prices, a depreciation of the domestic currency, and increases in inflation expectations. Once CBI and RN components are isolated, however, these anomalies largely disappear. In response to contractionary pure target-rate shocks, output and prices exhibit a hump-shaped decline, the domestic currency appreciates against the U.S.\ dollar, and inflation expectations remain well anchored. In addition, stock prices decline, and both the
one-year rate and the ten-year yield increase on impact, with the long-term yield rising by
a smaller amount. Overall, these responses are broadly consistent with standard monetary
transmission mechanisms and closely aligned with the empirical evidence for AEs.

The responses to CBI and RN shocks identified from target-rate surprises help shed light on these findings and clarify the role of each component in biasing the transmission of conventional MP shocks. In particular, favorable CBI shocks are associated with increases in interest rates, expansions in output, higher prices, rising inflation expectations, and a depreciation of the Mexican peso. These responses appear to be consistent with a scenario in which the central bank reveals favorable information about economic fundamentals while simultaneously tightening policy to contain emerging inflationary pressures. Hawkish RN shocks generate similar dynamics and may therefore capture episodes in which the central bank tightens policy more aggressively than markets had anticipated in response to observable improvements in economic conditions. In both cases, the contractionary effects of tighter monetary policy appear to be offset by the expansionary forces associated with the underlying macroeconomic developments. Thus, failing to disentangle CBI and RN components may lead to biased estimates of monetary policy effects.




The results for unconventional MP shocks differ in several respects. The impulse responses to contractionary FG shocks do not appear to exhibit a clear attenuation bias potentially arising from RN and CBI components, with the possible exception of inflation expectations, which tend to rise in the short run. Compared with pure target-rate shocks, however, unpurged FG shocks are associated with a disproportionately large and more immediate contraction in domestic activity. While these results could point to a more important role for FG in shaping macroeconomic outcomes, they may also reflect the amplification associated with the \emph{FG puzzle} discussed in the theoretical literature (see \hyperlink{Del Negro et al. (2023)}{Del Negro et al., 2023}), whereby revisions in expectations about the future policy path tend to generate macroeconomic effects that are disproportionately large relative to those of conventional MP shocks. At the same time, the relatively rapid response of output contrasts with the conventional view that monetary policy affects real activity with substantial lags.


Once RN and CBI components are isolated, however, the effects of FG shocks become more moderate and closely resemble those of pure target-rate shocks. Notably, the large and almost immediate decline in output largely disappears. In addition, inflation expectations exhibit a more muted response and appear to remain better anchored following the unconventional policy shock. These results are more consistent with the evidence reported by \hyperlink{Solis (2023b)}{Solís (2023b)}, who shows that FG surprises play an equally important role as target-rate surprises in the transmission of monetary policy to financial markets in Mexico. They also broadly align with the international evidence reported by \hyperlink{Andrade and Ferroni (2021)}{Andrade and Ferroni (2021)} and \hyperlink{Swanson (2021, 2024)}{Swanson (2021, 2024)}, who find that FG shocks tend to generate macroeconomic effects comparable to those of conventional policy shocks.

In general, the impulse responses to CBI and RN shocks identified from FG surprises do not differ markedly from those of pure FG shocks, further suggesting that attenuation bias through these channels  is limited in the case of FG. One possible interpretation is that the central bank responds to evolving demand conditions primarily through adjustments in the policy rate rather than through communication about the future policy path. This behavior may reflect the fact that, in EMEs, FG has typically been used as a complementary rather than a primary policy tool. Unlike in AEs—where central banks were constrained by the effective lower bound and relied more heavily on this unconventional tool—FG in EMEs tends to reinforce and complement policy rate decisions, rather than substitute for them. As a result, CBI and RN shocks may play a more prominent role in attenuating the effects of target-rate surprises than those of FG surprises.

One aspect worth highlighting, however, is the response of domestic output to hawkish RN shocks identified from FG surprises. The dynamics closely resemble those following unpurged FG shocks, suggesting that the amplified and rapid effects of such shocks on economic activity partly reflect RN contamination. One plausible interpretation is that, in the context of FG, market participants tend to overestimate the central bank’s reaction function. For instance, when economic activity is weakening, investors may anticipate a strongly accommodative policy path, whereas the central bank—consistent with the behavior discussed above and its primary mandate of price stability—signals a relatively more hawkish stance or provides little additional guidance due to concerns about inflationary pressures. The resulting impulse responses would then reflect both the contractionary effects of an upward revision in the expected path of policy rates and underlying weakness in output that was already underway, thereby generating disproportionately large and front-loaded declines in activity.

This paper contributes to the literature along three main dimensions. First, it complements \hyperlink{Jarociński and Karadi (2025)}{Jarociński and Karadi (2025)}, who jointly analyze the role of CBI and RN shocks in shaping monetary policy transmission in the U.S., by extending their framework to an EME and examining how these shocks affect the transmission of both conventional and unconventional monetary policy. We show that RN shocks play distinct contamination roles across policy instruments: they tend to attenuate—or even reverse—the effects of target-rate surprises, while amplifying and accelerating the transmission of FG surprises. 

Second, this paper provides new evidence on the macroeconomic effects of FG in EMEs, a dimension that has received relatively limited attention in the existing literature. In particular, we complement \hyperlink{Solis (2023b)}{Solís (2023b)}, who shows that target-rate and FG surprises play a similarly important role in the transmission of monetary policy to financial markets in Mexico. We show that, once purified of CBI and RN components, these surprises also have comparable effects on macroeconomic variables such as output, prices, and inflation expectations. 

Third, we propose an alternative and complementary explanation for several puzzles documented in the literature on monetary transmission in EMEs, where HFI-based evidence has reported counterintuitive responses of exchange rates, prices, and inflation expectations to contractionary MP shocks. We show that these puzzles may arise from failing to disentangle CBI and RN components embedded in interest rate surprises.

The remainder of the paper is organized as follows. \hyperlink{Section 2}{Section~2} reviews the related literature. \hyperlink{Section 3}{Section~3} outlines the construction of monetary policy surprises and the identification strategy used to isolate the shocks of interest. \hyperlink{Section 4}{Section~4} presents the VAR and the data used in the estimation. The empirical results are reported in \hyperlink{Section 5}{Section~5}. \hyperlink{Section 6}{Section~6} concludes.

% Smart bibliography: Only include bibliography if standalone AND has citations
\smartbib

\end{document}
