\input{./._relpath-to-latexroot.ltx}
\documentclass[\latexroot/\projectname]{subfiles}
\input{\latexroot/@resources/subfile-setup.ltx}
\begin{document}

\whenintegrated{\label{microeconomic-literature}}\par\section{Related literature}
\whenintegrated{\label{sec:microlit}} % integrated doc: SST for labels

This paper relates to the growing body of work that uses HFI to study the macroeconomic effects of monetary policy. Building on early contributions such as \hyperlink{Kuttner (2001)}{Kuttner (2001)} and \hyperlink{Gürkaynak et al. (2005)}{Gürkaynak et al. (2005)}, a large literature combines interest rate surprises with VARs  to estimate the effects of conventional and unconventional MP shocks (e.g., \hyperlink{Gertler and Karadi (2015)}{Gertler and Karadi (2015)};  \hyperlink{Andrade and Ferroni (2021)}{Andrade and Ferroni (2021)}; \hyperlink{Miranda-Agrippino and Ricco (2021)}{Miranda-Agrippino and Ricco (2021)}; \hyperlink{Bauer and Swanson (2023a, 2023b)}{Bauer and Swanson (2023a, 2023b)}; \hyperlink{Swanson (2021, 2024)}{Swanson (2021, 2024)}; \hyperlink{Jarociński and Karadi (2020, 2025)}{Jarociński and Karadi (2020, 2025)}).

In particular, a growing body of research aims to quantify the role of CBI and RN shocks in contaminating interest rate surprises. \hyperlink{Jarociński and Karadi (2020)}{Jarociński and Karadi (2020)} exploit the high-frequency co-movement between interest rate and stock price surprises around FOMC announcements to distinguish between MP and CBI shocks. Their results show that interest rate surprises purged of CBI effects generate a more pronounced contraction in activity and prices than their unpurged counterparts. \hyperlink{Bauer and Swanson (2023a, 2023b)}{Bauer and Swanson (2023a, 2023b)} propose purging interest rate surprises of the component predicted by public news, which reflects RN shocks. MP shocks identified in this way generate stronger contractionary effects. Building on these two strands of the literature, \hyperlink{Jarociński and Karadi (2025)}{Jarociński and Karadi (2025)} propose a unified framework that jointly identifies MP, CBI, and RN shocks. Applying this approach to the U.S., they find robust evidence of CBI shocks but limited evidence that RN shocks play an important role in contaminating interest rate surprises. 

Our paper complements this research by applying the \hyperlink{Jarociński and Karadi (2025)}{Jarociński and Karadi (2025)} framework to an EME and by jointly analyzing the macroeconomic effects of MP, CBI, and RN shocks embedded in both target-rate and FG surprises. We show that both CBI and RN components play an important role in contaminating the transmission of target-rate surprises by attenuating and even reversing their estimated effects. Notably, for FG surprises, RN components appear to distort the estimated transmission by disproportionately amplifying and accelerating their effects, particularly on output, while CBI components mainly generate a small attenuation bias in the response of inflation expectations.



We also contribute to the literature that analyzes the macroeconomic effects of FG. For AEs, \hyperlink{Campbell et al. (2012)}{Campbell et al. (2012)} and \hyperlink{Andrade and Ferroni (2021)}{Andrade and Ferroni (2021)} emphasize that FG surprises may combine “Odyssean” policy commitments with “Delphic” signals about future macroeconomic conditions. \hyperlink{Andrade and Ferroni (2021)}{Andrade and Ferroni (2021)} show that these “Delphic” signals can reverse the estimated effects of FG shocks on prices, expectations, and credit spreads. By contrast, for real activity, these signals do not appear to generate a clear attenuation bias. \hyperlink{Swanson (2024)}{Swanson (2024)} shows that FG surprises in the U.S. may be contaminated by RN components, which tend to attenuate their estimated macroeconomic effects. For the particular case of Mexico, \hyperlink{Solis (2023b)}{Solís (2023b)} shows that interest rate surprises contain two distinct dimensions—target-rate and FG surprises—that play a similarly important role in the transmission of monetary policy to financial markets. 

We complement \hyperlink{Solis (2023b)}{Solís (2023b)} by disentangling target-rate and FG surprises into MP, CBI, and RN components and by examining their macroeconomic effects on variables such as output, prices, and inflation expectations. In doing so, we also complement the evidence in \hyperlink{Swanson (2024)}{Swanson (2024)} by showing that, in the context of an EME, RN components may disproportionately amplify and accelerate the effects of FG shocks. In line with \hyperlink{Andrade and Ferroni (2021)}{Andrade and Ferroni (2021)}, we find that CBI shocks tend to attenuate the estimated effects of FG shocks on inflation expectations, but do not play a significant role in biasing their transmission to real activity.

Finally, this paper contributes to the literature on monetary transmission in EMEs, where empirical work using HFI has documented puzzling responses of exchange rates, prices, and inflation expectations to contractionary MP shocks. \hyperlink{Aruoba et al. (2021)}{Aruoba et al. (2021)} show that the domestic currency depreciates and inflation expectations rise following an unexpected tightening in Chile. Using a panel of EMEs, \hyperlink{Bolhuis et al. (2024)}{Bolhuis et al. (2024)} document an average depreciation of the exchange rate after contractionary MP shocks. More recently, \hyperlink{Witheridge (2024)}{Witheridge (2024)} reports increases in prices and inflation expectations following an unexpected tightening and interprets them as evidence of fiscal-led policy dynamics in some EMEs, including Mexico. \hyperlink{Solís (2023a)}{Solís (2023a)} also finds evidence of an exchange rate puzzle in Mexico but shows that it largely disappears when the exchange rate response around monetary policy announcements is measured using intraday data.

We contribute to this literature by proposing an alternative and complementary explanation for the emergence of these puzzles: the failure to account for informational components embedded in interest rate surprises. We show that once CBI and RN components are isolated, impulse responses to an MP shock become broadly consistent with standard transmission mechanisms. Importantly, we conduct the analysis using daily data, which is particularly valuable in EMEs where access to intraday financial data may be limited.
% Smart bibliography: Only include bibliography if standalone AND has citations
\smartbib

\pdfonly{
% execute this version if compiling with pdflatex
\end{document}
}
